\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
rewording stuff

To demonstrate how easily AORTA can be utilized to evaluate different
intersection policies, this section presents a simple experiment showing how
different policies affect the throughput of intersections. In this experiment,
every intersection in the map uses either a stop sign, traffic signal, or
autonomous reservation policy.

@@

The experiment simulates a 9$\times$11km$^{2}$ slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, for one hour. The step duration is fixed at
0.1 seconds. While the intersection policies vary, the agents spawned and their
routes remain the same. A generator creates one new agent every 1 simulation
second, with a uniformly random starting position and goal.

@@

If an intersection immediately permits an agent to proceed and grants other
agents in the same lane similar access (because this new agent must still follow
these others), then the new agent may simply proceed at full speed limit without
pausing. This gives the least possible delay spent along some lane, so any extra
time is defined as lag and is used to measure intersection performance. Figure
\ref{fig:avg_lag} graphs the average of this delay per agent. On average,
reservation policies cause less than 1 second of delay at each intersection,
stop signs cause about 7 seconds lag, and traffic signals using the heuristic
described above cause 16 seconds. These results will vary with different
traffic levels and policy configurations, so the important demonstration is that
AORTA can be used as a framework for evaluating these policies.

>>>>

This section presents a simple experiment showing how different policies affect
the throughput of intersections. In this experiment, every intersection in the
map uses either a stop sign, traffic signal, or autonomous reservation policy.
The results demonstrate that policies affect total system performance and that
AORTA is a useful tool for evaluating this relation.

@@

The experiment simulates a 9$\times$11km$^{2}$ slice of downtown Austin,
Texas\footnote{bounded by the Mopac and Springdale Road horizontally, and Oltorf
Street and Koenig Lane vertically}, and a 15$\times$13km$^{2}$ slice of downtown
Houston, Texas \footnote{bounded by Ella Boulevard and Eastex Freeway
horizontally, and West Alabama Street and Crosstimbers Street vertically}, for
one hour. The step duration is fixed at 0.1 seconds. While the intersection
policies vary, the agents spawned and their routes remain the same.  A generator
creates one new agent every 1 simulation second, with a uniformly random
starting position and goal.

@@

If an agent travels along a lane at the speed limit and does not slow down to
wait at an intersection, then it traverses the lane in an optimal amount of
time. If the intersection orders it to stop or if other agents in the same lane
have slowed down by the intersection's orders, then the intersection has caused
some delay. This delay can be used as one measure of intersection performance.
Figures \ref{fig:avg_lag_atx} and \ref{fig:avg_lag_houston} graph the average of
this delay per agent. On average, reservation policies cause less than 1 second
of delay at each intersection, stop signs cause about 7 seconds lag, and traffic
signals using the heuristic described above cause 16 seconds. These results will
vary with different traffic levels and policy configurations, so the important
demonstration is that AORTA can be used as a framework for evaluating these
policies.
